Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-07 Code/Manuscript_O2.Rmd
fixed fig caps

MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

@@

SS120GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

@@

MIT9313GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

@@

                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
                    "Colors represent the actinic spectral waveband (nm).",
                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles",

>>>>

MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

SS120GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
                    "Colors represent the actinic spectral waveband (nm).",
                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
